% --- Abstract in English ---
\begin{otherlanguage}{english}
\begin{abstract}
\noindent % No indent for the first line of abstract
% ABSTRACT
% Last Name First Name Patronymic. Master's Thesis Title. — Manuscript.
% 
% Thesis for the Master's degree in specialty XXXXXX "Specialty Name" — 
% University Name, City, Year.

The Master's thesis is devoted to the development of the full-stack web application \textit{Beekeepers Community Platform}, designed to unite beekeepers for knowledge and experience exchange.

The work includes an analysis of the subject area, a review of existing solutions for communities, and a justification for the chosen technology stack, which includes React for the frontend, NestJS for the backend, and MongoDB as the database.

The system architecture was designed, and functional and non-functional requirements were defined. Key modules have been developed, such as a forum for discussions, a knowledge base, an interactive map for managing apiaries and fields, and a user authentication system with email verification and Google Sign-In capability.

The development process, code structure, API design principles, and main system components are described. Security considerations were addressed, and appropriate mechanisms were implemented.

Testing of the main functional capabilities of the application was conducted. Based on the results, conclusions were formulated, and directions for further platform development were outlined.

\textbf{Keywords:} web application, beekeepers community, React, NestJS, MongoDB, forum, knowledge base, interactive map, authentication, OAuth.
\end{abstract}
\end{otherlanguage} 